\LARGE Tailoring Differentially Private Bayesian Inference to Distance Between Distributions

### 2018-10-11 TPDP2018/poster/main.tex
some more work on the poster

  \begin{block}{Preliminary Experimental Results}
    Experiments are on three mechanisms and plotted as follows:
\begin{itemize}
  \item[-] {\textbf{\color{green}{Green}}}: Baseline approach. %adds noise scaled to sensitivity proportional to dimensionality,
  \item[-] {\textbf{\color{red}{Red}}}: Improved baseline approach with sensitivity $1$ in 2 dimensions and $2$ in higher dimensions, since it's equivalent to histogram problem 
  (posteriors of adjacent data sets differ only in two dimensions).
  \item[-] {\textbf{\color{blue}{Blue}}}: $\hexpmech$.
\end{itemize}
% In Fig. \ref{subfig_concrete_prob_2d} and \ref{subfig_concrete_prob_3d} we plot on the x-axis the Hellinger distance from the true posterior and on the y-axis the
% probability of the distributions with that distance under the different mechanisms. In Fig. \ref{subfig_prior} we present the influence of the prior on the accuracy of the three mechanisms,
% by showing the quartiles of the experimental distribution of the Hellinger distance.
\begin{figure}[H]
\begin{center}
\centering
  \subfigure[2 dimensions with data size $600$]{
    \includegraphics[width=0.31\textwidth]{poster_5.eps}
  \label{subfig_concrete_prob_2d}
  }
  \subfigure[3 dimensions with data size $600$]{
    \includegraphics[width=0.31\textwidth]{poster_6.eps}
  \label{subfig_concrete_prob_3d}
  } 
\subfigure[2 dimensions with data size $100$]{
    \includegraphics[width=0.313\textwidth]{poster_4.eps}
  \label{subfig_prior}
  }

@@

\begin{itemize}
  \item[-] The $\hexpmech$ outperforms asymptotically the baseline 
  approach but not the improved one.
  \item[-] By increasing the prior, $\hexpmech$ can outperform LapMech under small data set size.
  % \begin{enumerate}
  %   \item  The accuracy that we are going to explore next, and in a more principled and formal way.

>>>>

  \begin{block}{Preliminary experimental results}
    Experiments are about three mechanisms and plotted as follows:
\begin{itemize}
  \item[-] {\textbf{\color{green}{Green}}}: Baseline approach. %adds noise scaled to sensitivity proportional to dimensionality,
  \item[-] {\textbf{\color{red}{Red}}}: Improved baseline approach with sensitivity 1 in 2 dimensions and 2 in higher dimensions.
    Indeed: the number of elements in every bin always sums up to $n$ and hence $||\bysinfer(x)-\bysinfer(x')||_1\leq 2$, when $\adj{x}{x'}$.

  \item[-] {\textbf{\color{blue}{Blue}}}: $\hexpmech$.
\end{itemize}
% In Fig. \ref{subfig_concrete_prob_2d} and \ref{subfig_concrete_prob_3d} we plot on the x-axis the Hellinger distance from the true posterior and on the y-axis the
% probability of the distributions with that distance under the different mechanisms. In Fig. \ref{subfig_prior} we present the influence of the prior on the accuracy of the three mechanisms,
% by showing the quartiles of the experimental distribution of the Hellinger distance.
\begin{figure}[H]
\begin{center}
\centering
  \subfigure[2 dimensions with data size $600$]{
    \includegraphics[width=0.31\textwidth]{poster_5.eps}
  \label{subfig_concrete_prob_2d}
  }
  \subfigure[3 dimensions with data size $600$]{
    \includegraphics[width=0.31\textwidth]{poster_6.eps}
  \label{subfig_concrete_prob_3d}
  } 
\subfigure[2 dimensions with data size $100$]{
    \includegraphics[width=0.313\textwidth]{poster_4.eps}
  \label{subfig_prior}
  }

@@

\begin{itemize}
  \item[-]  $\hexpmech$ outperforms the baseline approach but not the improved one.
  \item[-] By increasing the prior, $\hexpmech$ can outperform both the baseline approach and the improved one.
  % \begin{enumerate}
  %   \item  The accuracy that we are going to explore next, and in a more principled and formal way.
